Untwisting the Tetrahelix (v0.7)

### 2017-02-28 doc/TetrahelixUntwist.tex
addition of math and function for inradius, and a major bug fixed

\title{Untwisting the Tetrahelix (v0.6)}
\author{Robert L. Read \texttt{read.robert@gmail.com} \and
  Robert Gatliff \texttt{robert@toubat.org}
}

@@

\begin{theorem}
  Any optimal tetrahelix has all vertices on a single cylinder.
\end{theorem}

@@

Figure\ref{untouchingrailfig} depicts a projection of
depicting only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
and the intermediary points $R$ and $Q$ on the other two rails.

@@

@@

>>>>

\title{Untwisting the Tetrahelix (v0.7)}
\author{Robert L. Read \texttt{read.robert@gmail.com} \and
  Robert Gatliff \texttt{robert@toubat.org}
}

@@

\begin{theorem}
  \label{thm:cylinder}
  Any optimal tetrahelix has all vertices on a single cylinder.
\end{theorem}

@@

Figure \ref{untouchingrailfig} depicts a projection of
depicting only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
and the intermediary points $R$ and $Q$ on the other two rails.

@@

Theorem \ref{thm:cylinder} is not true when $\rho$ is an odd multiple of $\pi$.

@@

If you look down the axis of an optimal tetrahelix, it happens that only the one-hop edges
come closest to the axis. In other words, they define the radius of the incircle of the
projection, or the radius of a cylinder that would just fit inside the tetrahelix.
This is useful to know if the tetrahelix is used as a structure to house a pipe or
a ladder or that must bear a human or to armor a conduit. The \emph{inradius} of
an optimal tetrahelix is a function of the radius $r$ and the rail angle $\rho$:
\begin{equation}
  \label{eq:inradius}
  \frac{r \sin{(\pi - \rho)}}{6}
\end{equation}
Which can be seen from the trigonometry of the projection diagram:

\begin{figure}[H]
  \label{projectiondiagram}
     \centering
     \includegraphics[width=0.3\textwidth]{figures/ProjectionDiagram.png}
     \caption{Projection Diagram (needs labels)}
\end{figure}
